\begin{frame}{Family of free GNU Multiple Precision Libraries}

\begin{itemize}\itemsep0.5em

\item
\textbf{GMP - GNU Mult. Prec. Arithmetic Library}\footnote{\tiny
\url{https://gmplib.org/}}
(C/C++, version 6.2.1; since 1991)
\begin{itemize}
\item
supports: signed integers, rational numbers, and floating-point numbers

\item
arithmetic and logic functions for supported data types

\item
focus: \textbf{speed, cryptography}
\end{itemize}

\item
\textbf{MPFR - GNU Mult. Prec. Fl.-Point Reliable Library}\footnote{\tiny
\url{https://www.mpfr.org/}}
(C, version 4.1.0; since 2000)
\begin{itemize}
\item
supports: floating-point numbers (arithmetic and logic functions)

\item
focus: \textbf{correct rounding}, precise semantics (IEEE 754)
\end{itemize}

\item
\textbf{MPC - GNU Mult. Prec. Complex Library}\footnote{\tiny
\url{http://www.multiprecision.org/}}
(C, version 1.2.1; since 2003)
\begin{itemize}
\item
addition: \textbf{complex} floating-point numbers
\end{itemize}

\bigskip

\item
Many interfaces (C++, Python, ...) are available.

\end{itemize}

\end{frame}



\begin{frame}{Comparable Matlab/Octave toolboxes}

\begin{itemize}\itemsep0.5em

\item
\textbf{Matlab VPA (Variable-precision arithmetic,
Symbolic toolbox)}\footnote{\tiny
\url{https://www.mathworks.com/help/symbolic/vpa.html}}
\begin{itemize}
\item
Slow for dimensions > 200.
\end{itemize}

% Pavel Holoborodko (Yokohama, Japan)
\item
\textbf{Advanpix}\footnote{\tiny
\url{https://www.advanpix.com/}}
(version 4.8.5.14569; since 2010)
{\color{red} Very fast and complete!}
\begin{itemize}
\item
{\color{blue} closed source} (P-code), proprietary license

\item
Matlab only
\end{itemize}

% Jean-Daniel Bancal (Switzerland)
\item
\textbf{GEM - Gmp Eigen Matrix Library}\footnote{\tiny
\url{https://gem-library.github.io/}}
(version 2.0.2; since 2016)
\begin{itemize}
\item
free, open source (MPL-2.0, others)

\item
Matlab and Octave
\end{itemize}

% Ben Barrowes (USA)
\item
\textbf{mptoolbox}\footnote{\tiny
\url{https://sourceforge.net/projects/mptoolbox/}
and
\url{https://www.mathworks.com/matlabcentral/fileexchange/6446-multiple-precision-toolbox-for-matlab}}
(version 1.5; since 2004)
\begin{itemize}
\item
free, open source (BSD-3-Clause)

\item
Matlab and "Octave" (needs some adaptions)
\end{itemize}

\end{itemize}

\end{frame}
